First exclusive Deeply Virtual Compton Scattering measurement off bound nucleon in $^4$He

### 2018-03-28 eg6-letters/incoherent/incoherent_prl.tex
cleaning the paper after updating the incoherent ratio plot

\begin{figure}[tb]
\centering
\includegraphics[width=6.9cm]{figs/ALU_ratioInc_Q2_shortscenrario.pdf}\\
\includegraphics[width=6.9cm]{figs/ALU_ratioInc_x_shortscenrario.pdf}\\
\includegraphics[width=6.9cm]{figs/ALU_ratioInc_t_shortscenrario.pdf}
\caption{ The $A_{LU}$ ratio of the bound to the free proton at 
   $\phi$~=~90$^{\circ}$, as a function of $Q^2$ (top), $x_B$ (middle), and $t$ 
   (bottom). The black squares are from this work, the green circles are the 
HERMES inclusive measurement \cite{Airapetian:2009cga}. The blue and red curves 
are results of off-shell calculations \cite{simonetta_2}. The solid and dashed 
black curves are from on-shell calculations \cite{Guzey:2008fe}.} 
\label{fig:incoh_EMC_ratio_ALU_proton}
\end{figure}

>>>>

\begin{figure}[tb]
\centering
%\includegraphics[width=6.9cm]{figs/ALU_ratioInc_Q2_shortscenrario.pdf}\\
%\includegraphics[width=6.9cm]{figs/ALU_ratioInc_x_shortscenrario.pdf}\\
\includegraphics[width=8.5cm]{figs/ALU_ratioInc_t_shortscenrario.pdf}
\caption{ The $A_{LU}$ ratio of the bound to the free proton at 
   $\phi$~=~90$^{\circ}$ as a function of $t$. The black squares are from this 
   work, the green circles are the HERMES inclusive measurement 
   \cite{Airapetian:2009cga}. The blue and red curves are results of off-shell 
   calculations \cite{simonetta_2}. The solid and dashed black curves are from 
   on-shell calculations \cite{Guzey:2008fe}.} 
   \label{fig:incoh_EMC_ratio_ALU_proton}
\end{figure}
